Flexibility of interactions depends on habitat suitability

### 2019-07-30 paper/manuscript.Rmd
Abstract attempt

Ecological interactions could also vary with the environment, P(Lijy | Ey ). Although it is rare to see a con- ditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment. For instance, McKinnon et al. (2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north. It is also common to see increasing top-down control with temperature (Shurin et al. 2012, Gray et al. 2016). Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al. 2007, Petchey et al. 2010, Woodward et al. 2010).

>>>>

Ecological interactions could also vary with the environment. Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment. For instance, McKinnon et al. (2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north. It is also common to see increasing top-down control with temperature (Shurin et al. 2012, Gray et al. 2016). Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al. 2007, Petchey et al. 2010, Woodward et al. 2010).
